### 2023-03-30 manuscript.tex
update data availability [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/ed68e62ce4e8fd69a528319870ab7e5ce2c2abc8.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/ed68e62ce4e8fd69a528319870ab7e5ce2c2abc8/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/4565067201

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/92e94ee4307718776393434199be15f82a344012/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/92e94ee4307718776393434199be15f82a344012}{MMV-Lab/im2im-paper@92e94ee}
on March 17, 2023.

@@

\hypertarget{code-and-data-availability}{%
\subsection{Code and data availability}\label{code-and-data-availability}}

@@

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/ed68e62ce4e8fd69a528319870ab7e5ce2c2abc8/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/ed68e62ce4e8fd69a528319870ab7e5ce2c2abc8}{MMV-Lab/im2im-paper@ed68e62}
on March 30, 2023.

@@

\hypertarget{code-availability-and-requirements}{%
\subsection{Code availability and requirements}\label{code-availability-and-requirements}}

@@

\hypertarget{data-availability}{%
\subsection{Data availability}\label{data-availability}}

All data used in this work were from public repositories, released with other publications. The scripts we used to download and re-organize the data can be found in our release repository: https://github.com/MMV-Lab/mmv\_im2im/tree/main/paper\_configs/prepare\_data
